Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 Discussion.tex
onto 12 pages

The proofs of Theorem~\ref{rst:budget} and Theorem~\ref{rst:regret} incur exponential (in \ARMNUM) payment and regret in the initial phases because the threshold required for incentivization $1/\log(s)$ decreases slowly.
This slow decrease is needed to bound the regret in the later phases when the concentration inequality kicks in as in Equation~(\ref{equ:small_regret_bound}).
In this section, we discuss two restrictions on the problem setting under which  we can modify the algorithm slightly and provide stronger bounds, avoiding this exponential dependence.
Both problem settings are special cases of the more general problem setting previously considered.

@@

\begin{theorem}
\label{rst:discrete}
Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment budget bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
\end{align*}
and expected regret bounded above by 
\begin{align}
O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
  \right).  \nonumber
\end{align}
\end{theorem}

@@

When this assumption holds, we choose a different modification in the definition of payment eligibility.
Let $s_0 = \exp(2/\MinProb)$.
An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
if both of the following hold:
\begin{itemize}
\item $i$ has been pulled at most
$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s+s_0)$.
\end{itemize}

@@

\begin{theorem}
\label{rst:known-p}
Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has expected payment budget bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
\end{align*}
and expected regret bounded above by
\begin{align*}
O \left(\frac{\MAXR \ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
  + \frac{\ARMNUM^2 d\MAXR}{\MinProb}
  + \frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
\end{align*}
\end{theorem}

>>>>

The proofs of Theorem~\ref{rst:budget} and Theorem~\ref{rst:regret} incur exponential (in \ARMNUM) payment and regret in the initial phases because the threshold required for incentivization $1/\log(s)$ decreases slowly.
This slow decrease is needed to bound the regret in the later phases when the concentration inequality kicks in as in Equation~(\ref{equ:small_regret_bound}).
In this section, we discuss two restrictions \pfdelete{on the problem setting} under which  we can modify the algorithm slightly and provide stronger bounds, avoiding this exponential dependence.
Both problem settings are special cases of the more general \pfdelete{problem} setting previously considered.

@@

\begin{theorem}
\label{rst:discrete}
Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment \pfdelete{budget} bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
\end{align*}
and expected regret bounded above by 
\begin{align}
O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
  \right).  \nonumber
\end{align}
\end{theorem}

@@

When this assumption holds, we choose a different modification in the definition of payment eligibility.
Let $s_0 = \exp(2/\MinProb)$.
An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
if both: \pfdelete{of the following hold:}
\begin{itemize}
\item $i$ has been pulled at most
$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s+s_0)$.
\end{itemize}

@@

\begin{theorem}
\label{rst:known-p}
Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has expected payment \pfdelete{budget} bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
\end{align*}
and expected regret bounded above by
\begin{align*}
O \left(\frac{\MAXR \ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
  + \frac{\ARMNUM^2 d\MAXR}{\MinProb}
  + \frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
\end{align*}
\end{theorem}

### 2018-06-06 algorithm_regret.tex
onto 12 pages

In the low-probability event, we simply 
bound the maximum regret by \MAXR.
Now, applying Lemma~\ref{lem:phase-length},
the total expected regret from large-regret steps is at most

\begin{equation*}
\sum_{s = 1}^T \frac{24 \ARMNUM d}{T^2} \cdot \MAXR \cdot \ARMNUM \log(s)
\leq 12 \ARMNUM^2 d \MAXR.
\end{equation*}
%\pfcomment{I deleted the left-hand side of the above equation because it was using random terms in the summand, and actually wasn't true.  What was intended was an expectation outside of the sum, but I thought it simpler just to delete that term.}

Adding all four types of regret terms,
and substituting that 
$\EarlyCut[2]{s} = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
the cumulative regret up to time $T$ is at most

\begin{align*}
\lefteqn{O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \MAXR \log^2(T)
+ \ARMNUM^2 \MAXR d
+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)}
\\ & = 
O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \TieDensity \cdot \log^3(T) \right).\QED
\end{align*}
\end{emptyextraproof}

>>>>

In the low-probability event, we simply 
bound the maximum regret by \MAXR.
Now, applying Lemma~\ref{lem:phase-length},
the total expected regret from large-regret steps is at most
$\sum_{s = 1}^T \frac{24 \ARMNUM d}{T^2} \cdot \MAXR \cdot \ARMNUM \log(s)
\leq 12 \ARMNUM^2 d \MAXR.$
%\pfcomment{I deleted the left-hand side of the above equation because it was using random terms in the summand, and actually wasn't true.  What was intended was an expectation outside of the sum, but I thought it simpler just to delete that term.}

Adding all four types of regret terms,
and substituting 
$\EarlyCut[2]{s} = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
the cumulative regret up to time $T$ is at most
$
O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \MAXR \log^2(T)
+ \ARMNUM^2 \MAXR d
+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)\\
= 
O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \TieDensity \cdot \log^3(T) \right)$.\QED
\end{emptyextraproof}
